Generalized spaces for constructive algebra

### 2020-03-25 slides-herrsching2019.tex
typo

@@

@@

  \jnote{1}{
    The book is \fixedhref{https://arxiv.org/abs/1605.04832}{available on the
    arXiv} and warmly recommended, as are all slides by Thierry Coquand on
    constructive algebra.«
  }
\end{frame}
\addtocounter{framenumber}{-1}

>>>>

% XXX In note slides, explain "iff*".

@@

% XXX in note slides, explain which space X to take

@@

  \jnote{1}{
    The book is \fixedhref{https://arxiv.org/abs/1605.04832}{available on the
    arXiv} and warmly recommended, as are all slides by Thierry Coquand on
    constructive algebra.
  }
\end{frame}
\addtocounter{framenumber}{-1}
